Useful R tidbits: Social Networks

### 2022-03-20 _academics/ps753-useful-r-tidbits/ps753-useful-r-tidbits.Rmd
Specify package for sna::evcent and bonpow

# statnet version
climinfl.nodes <- data.frame(
    name      = climinfl.stat %v% "vertex.names",
    totdegree = sna::degree(climinfl.stat),
    indegree  = sna::degree(climinfl.stat, cmode = "indegree"),
    outdegree = sna::degree(climinfl.stat, cmode = "outdegree"),
    eigen     = evcent(climinfl.stat, ignore.eval = TRUE),
    bonanich  = bonpow(climinfl.stat),
    centr_clo = sna::closeness(climinfl.stat, gmode = "graph"),
    centr_btw = sna::betweenness(climinfl.stat, gmode = "graph")
)
# Network-level measures:
#   closeness centralization
climinfl.centr_clo = centralization(climinfl.stat, FUN = "closeness", mode = "graph")
#   betweenness centralization
climinfl.centr_btw = centralization(climinfl.stat, FUN = "betweenness", mode = "graph")

>>>>

# statnet version
climinfl.nodes <- data.frame(
    name      = climinfl.stat %v% "vertex.names",
    totdegree = sna::degree(climinfl.stat),
    indegree  = sna::degree(climinfl.stat, cmode = "indegree"),
    outdegree = sna::degree(climinfl.stat, cmode = "outdegree"),
    eigen     = sna::evcent(climinfl.stat, ignore.eval = TRUE),
    bonanich  = sna::bonpow(climinfl.stat),
    centr_clo = sna::closeness(climinfl.stat, gmode = "graph"),
    centr_btw = sna::betweenness(climinfl.stat, gmode = "graph")
)
# Network-level measures:
#   closeness centralization
climinfl.centr_clo = centralization(climinfl.stat, FUN = "closeness", mode = "graph")
#   betweenness centralization
climinfl.centr_btw = centralization(climinfl.stat, FUN = "betweenness", mode = "graph")
